---
title: "Shiny Application and Reproducible"
author: "Yeoh Eik Den"
date: "2/4/2017"
output: ioslides_presentation
---

## Instruction

First, you will create a Shiny application and deploy it on Rstudio's servers. Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.

## Setup Library
Total sample of Manual and Automatic car comparison
```{r}
library(shiny)
library(datasets)
library(dplyr)

head(mtcars)
mtcars<- mutate(mtcars, Transmission = ifelse(am==0, "Automatic", "Manual"))
hist(mtcars$am, main="Histogram for Automatic or Manual Cars", xlab="Cars")
```


## Reproducible Pitch Presentation

```{r}
library(ggplot2)

qplot(data=mtcars, x=rownames(mtcars), y=mpg, main="QPlot for Cars")
```



## URLs
Source code for ui.R and server.R files are available on the GitHub:https://github.com/eikden/eikden.github.io

Presentation Slide is available at: http://rpubs.com/eikden/shinyapplication

The app developed for the first part of the assignment is available at: https://eikden.shinyapps.io/MTCARS_Interaction_Demo/




